---
title: "2017 Baby weaning"
author: "IL, RSU, SU"
output:
  pdf_document:
    toc: yes
  html_notebook:
    fig_caption: yes
    toc: yes
    toc_float: yes
  word_document:
    toc: yes
---

# Data analysis

Data extracted was tabulated in a google sheet. Then exported as csv file and imported in R (R Core Team (2017). R: A language and environment for statistical computing. R  Foundation for Statistical Computing, Vienna, Austria. URL https://www.R-project.org/.)

The package meta was used for the meta-analysis. The heterogenicity between studies was checked with Tau2. A funnel plot was used to detect publication bias. We grouped the comparison and outcomes to compare studies. A random effect meta-analysis using odds-ratio as outcome was performed with a DerSimonian and Lard method (add reference DerSimonian 1986) . A forest plot was used to visualize the association between the exposure to specific risk factors and the outcome.  

Risk factors were grouped in reports focused to drink, food or breastfeeding and outcomes were severe early-childhood caries (s-ECC), white spot lesions (WSL) or caries measured in ICDAS>0. 


# Paquetes
```{r, include = F, echo = F}
Packages <- c("tidyverse", "forcats", "stringr", "broom", "meta")
lapply(Packages, library, character.only = TRUE)
rm(Packages)
```

# Dataset

```{r}
# df <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vR2cxtO3yvM7-qsEibr9s5dsWh-JCsItf0Vi1GkmKcxv9MxFqwLcbpoQdjEeAVWOpq7Q7EPzznqzdB0/pub?gid=0&single=true&output=csv")

df <- read_csv("2017-weaning.csv")
df <- mutate(df, Groups = paste(Comparison, Outcome))
df <- df %>% 
  filter(!str_detect(id, "Un Lam et al")) #avoid Un Lam papers

```




# ANALYSIS

## 1. Breastfeeding and s-ECC
### Selection of papers
```{r}
df_b_ecc <- df %>%
  filter(Groups == "Breastfeed S-ECC")
```

```{r}
meta1 <- metabin(`Events in A`, `Total in A`, 
                 `Events in B`, `Total in B`, 
                 data = df_b_ecc, #change this line 
                 sm="OR",  method.tau = "DL", 
                 comb.fixed = FALSE, 
                 studlab = id)
meta1
```

### Bias

```{r}
funnel.meta(meta1, 
            studlab = TRUE)
```

### Heterogeneity

Baujat B, Mahé C, Pignon JP, Hill C (2002), A graphical method for exploring heterogeneity in
meta-analyses: Application to a meta-analysis of 65 trials. Statistics in Medicine, 30, 2641–2652.

```{r}
baujat.meta(meta1, 
            yscale = 10, xmin = 2, ymin = 2, 
            cex.studlab = .55)
```

### Meta-analysis
```{r}
meta1 <- metabin(`Events in A`, `Total in A`, 
                 `Events in B`, `Total in B`, 
                 data = df_b_ecc, 
                 sm="OR",  method.tau = "DL", 
                 comb.fixed = FALSE, 
                 studlab = id)

```
```{r}
summary(meta1)
```
```{r}
meta1
```

#### Forest plot
```{r}
forest.meta(meta1, # layout = "JAMA", # JAMA layout is more simple 
       comb.fixed = FALSE,
       # LEFT
       label.left         = "Breastfeeding 1-23 mo", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "No Breastfeeding or >24 mo BF",
       col.label.right    = "darkred")
```


## 2.  Sugary drinks and s-ECC
### Selection of papers
```{r}
df_b_ecc <- df %>%
  filter(Groups == "Drink S-ECC")
df_b_ecc
```

```{r}
meta1 <- metabin(`Events in A`, `Total in A`, 
                 `Events in B`, `Total in B`, 
                 data = df_b_ecc, #change this line 
                 sm="OR",  method.tau = "DL", 
                 comb.fixed = FALSE, 
                 studlab = id)
```

### Bias

```{r}
funnel.meta(meta1, 
            studlab = TRUE)
```

### Heterogeneity

Baujat B, Mahé C, Pignon JP, Hill C (2002), A graphical method for exploring heterogeneity in
meta-analyses: Application to a meta-analysis of 65 trials. Statistics in Medicine, 30, 2641–2652.

```{r}
baujat.meta(meta1, 
            yscale = 10, xmin = 1, ymin = 1, 
            studlab = TRUE , 
            cex.studlab = .55)
```

### Meta-analysis
```{r}
meta1 <- metabin(`Events in A`, `Total in A`, 
                 `Events in B`, `Total in B`, 
                 data = df_b_ecc, 
                 sm="OR",  method.tau = "DL", 
                 comb.fixed = FALSE, 
                 studlab = id)

```
```{r}
summary(meta1)
```
```{r}
meta1
```

#### Forest plot
```{r}
df_b_ecc
forest.meta(meta1, # layout = "JAMA", # JAMA layout is more simple 
       comb.fixed = FALSE,
       # LEFT
       label.left         = "No sugary drinks", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "Sugary drinks",
       col.label.right    = "darkred")
```



## 3.  Food White and spot lesions
### Selection of papers
```{r}

df_b_ecc <- df %>%
  filter(Groups == "Food White spot lesions")
```

```{r}
meta1 <- metabin(`Events in A`, `Total in A`, 
                 `Events in B`, `Total in B`, 
                 data = df_b_ecc, #change this line 
                 sm="OR",  method.tau = "DL", 
                 comb.fixed = FALSE, 
                 studlab = id)
```

### Bias

```{r}
funnel.meta(meta1, 
            studlab = TRUE)
```

### Heterogeneity

Baujat B, Mahé C, Pignon JP, Hill C (2002), A graphical method for exploring heterogeneity in
meta-analyses: Application to a meta-analysis of 65 trials. Statistics in Medicine, 30, 2641–2652.

```{r}
baujat.meta(meta1, 
            yscale = 10, xmin = 1, ymin = 1, 
            studlab = TRUE , 
            cex.studlab = .55)
```

### Meta-analysis
```{r}
meta1 <- metabin(`Events in A`, `Total in A`, 
                 `Events in B`, `Total in B`, 
                 data = df_b_ecc, 
                 sm="OR",  method.tau = "DL", 
                 comb.fixed = FALSE, 
                 studlab = id)

```
```{r}
summary(meta1)
```
```{r}
meta1
```

#### Forest plot
```{r}
forest.meta(meta1, # layout = "JAMA", # JAMA layout is more simple 
       comb.fixed = FALSE,
       # LEFT
       label.left         = "No sugary snacks", 
       col.label.left     = "darkgreen", 
       # RIGHT
       label.right        = "Sugary snacks",
       col.label.right    = "darkred")
```



# References

```{r}
citation()
citation(package = "tidyverse")
citation(package = "stringr")
citation(package = "meta")
```